Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2021-05-20 paper/ifo-appendix.tex
getting manuscript ready for resubmission (removing identifying information for double anoymous review)
added Viterbi reference here as well

\section{Open-source code}
\label{app:code}
This project is implemented in Python 3~\cite{python} scripts and jupyter notebooks~\cite{jupyter,ipython} as well as in MATLAB~\cite{MATLAB}. We used the Python packages of numpy~\cite{numpy}, scipy~\cite{scipy}, matplotlib~\cite{matplotlib}, tqdm~\cite{tqdm}, and logmmse~\cite{logmmse}.
The current build and sample data can be found at:
%\textbf{[Removed GitHub web-link for double-anonymous review.]}
\url{https://github.com/daccordeon/gravexplain}
% \begin{verbatim}
% README
% \end{verbatim}

@@

This appendix contains some details regarding the implementation of the Viterbi algorithm described in Section~\ref{sec:viterbi}. 
The Viterbi algorithm is a classic method in signal processing, whose theoretical underpinnings and implementation are easily accessible to undergraduate students. 
The interested reader is referred to the excellent review paper by Rabiner~\cite{Rabiner:1989} and textbook by Quinn and Hannam~\cite{QuinnEtAl:2001} to learn more.

>>>>

\section{Open-source code}
\label{app:code}
This project is implemented in Python 3~\cite{python} scripts and jupyter notebooks~\cite{jupyter,ipython} as well as in MATLAB~\cite{MATLAB}. We used the Python packages of numpy~\cite{numpy}, scipy~\cite{scipy}, matplotlib~\cite{matplotlib}, tqdm~\cite{tqdm}, and logmmse~\cite{logmmse}.
The current build and sample data can be found at:
\textbf{[Removed GitHub web-link for double-anonymous review.]}
%\url{https://github.com/daccordeon/gravexplain}
% \begin{verbatim}
% README
% \end{verbatim}

@@

This appendix contains some details regarding the implementation of the Viterbi algorithm described in Section~\ref{sec:viterbi}. 
The Viterbi algorithm~\cite{Viterbi:1967} is a classic method in signal processing, whose theoretical underpinnings and implementation are accessible to undergraduate students. 
The interested reader is referred to the excellent review paper by Rabiner~\cite{Rabiner:1989} and textbook by Quinn and Hannam~\cite{QuinnEtAl:2001} to learn more.
